Inefficient Concessions and Mediation

### 2016-12-03 presentation.tex
finish presentation for Midwest Theory

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\pause
Conflict: Slantchev (2011), Arena (2013)
\pause
		\begin{itemize}[<+->]
			\item Commitment to peace, not resolve to fight
			\item Concessions are costly signals instead of bargaining chip
			\item Costly signals are concessions instead of proof of resolve
		\end{itemize}

\pause
Mediation: Fey and Ramsay (2008, 2011), Horner et al. (2010)
\pause
		\begin{itemize}
			\item Information is about ability to commit, not resolve
		\end{itemize}

@@

	\pause
	\vskip.2in
	\begin{itemize}[<+->]
		\item The smallest concession is $c_l^{-1}\left(p(T+D)\right)$
		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
	\end{itemize}
\end{frame}

@@

\begin{frame}[label=hurt]
\frametitle{Concessions can hurt the giver}
\pause
Now assume a low type will use concessions against you, i.e. to increase their payoffs from fighting \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
\vskip.1in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 4}
  There are parameters under which the optimal equilibrium features inefficient concessions.
\end{beamerboxesrounded}
\[
  U_h=(1-\de_h)(-g) + \de_h \left[pT(1+eg)+peg+(1-p)(W-D(1+eg))\right]
\]
\pause

\begin{itemize}[<+->]
	\item If $p$ is low, concessions likely to be used against you, so remove material value
	\item Conjecture: Pooling on `Fight' optimal over larger set of parameters
\end{itemize}
\end{frame}

\section{Mediation}
\subsection{}
\begin{frame}{Mediator as mechanism designer}
\pause
`Manipulative' mediator: parties report their types, must deliver the stipulated concessions
\pause
\begin{itemize}[<+->]
  \item Mechanism: if two high types, give concession and play `Trust'; Otherwise, no concession and `Fight'
	\item Concession is necessary to get truthful revelation
	\item Cost of concession must be greater than benefit for low type
\end{itemize}
\vskip.1in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
  A mediator can eliminate inefficient concessions.
\end{beamerboxesrounded}

>>>>

\documentclass{beamer} 
%\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\pause
Conflict: Slantchev (2011), Arena (2013)
\pause
		\begin{itemize}[<+->]
			\item Concessions are costly signals instead of bargaining chip
			\item Commitment to peace, not resolve to fight
			\item Costly signals are concessions instead of proof of resolve
		\end{itemize}

\pause
Mediation: Fey and Ramsay (2008, 2011), Horner et al. (2010)
\pause
		\begin{itemize}
			\item Information is about ability to commit, not resolve
		\end{itemize} 
\end{frame}

@@

\pause	
\[
  U_h=(p-1)g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT+(1-p)(W-D)\right]
\]
\pause
\vskip-.1in

	\begin{itemize}[<+->]
		\item The smallest concession is $c_l^{-1}\left(p(T+D)\right)$
		\item If $p$ is low, high types are better off in the `fight' pooling equilibrium
	\end{itemize}
\end{frame}

@@

\begin{frame}[label=hurt]
\frametitle{Concessions can hurt the giver}
\pause
Now assume a low type will use concessions against you, i.e. to reduce your payoffs when partner fights \hyperlink{Supplemental}{\beamerbutton{Modified Payoffs}}
\vskip.1in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 4}
  There are parameters under which the optimal equilibrium features inefficient concessions.
\end{beamerboxesrounded}
\pause
\[
  U_h=peg-g + \textstyle \frac{\de_h}{(1-\de_h)} \left[pT(1+eg)+(1-p)(W-D(1+eg))\right]
\]
\pause
\vskip-.1in
\begin{itemize}[<+->]
	\item If $p$ is low, concessions likely to be used against you, so remove material value
	\item Conjecture: Pooling on `Fight' optimal over larger set of parameters
\end{itemize}
\end{frame}

\section{Mediation}
\subsection{}
\begin{frame}{Mediator as mechanism designer}
\pause
`Manipulative' mediator: parties report their types, must deliver the stipulated concessions
\pause
\begin{itemize}[<+->]
  \item Mechanism: if two high types, give concession and play `Trust'; Otherwise, no concession and `Fight'
	\item Concession is necessary to get truthful revelation, but only to high type
	\item Cost of concession must be greater than benefit for low type
\end{itemize}
\vskip.1in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Theorem 5}
  A mediator can eliminate inefficient concessions.
\end{beamerboxesrounded}
